\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/amta2016.tex
authors

% \mtsummitHeader{x}{x}{xxx-xxx}{2016}{45-character paper description goes here}{Author(s) initials and last name go here}
\title{\bf Formatting Your Paper \\
  for the \confname~Conference}

\author{\name{\bf First Author} \hfill  \addr{author1@abc.university.country}\\ 
        \name{\bf Second Author} \hfill \addr{author2@abc.university.country}\\ 
        \addr{Department of Science, My University, 
        MyTown, Zip, Country}
\AND
       \name{\bf Third Author} \hfill \addr{author3@abc.university.country}\\
        \addr{Department of Science, My University, 
        MyTown, Zip, Country}
}

>>>>

% \mtsummitHeader{x}{x}{xxx-xxx}{2016}{45-character paper description goes here}{Author(s) initials and last name go here}
\title{\bf Fast, Scalable Phrase-Based SMT Decoding}

\author{\name{\bf Hieu Hoang} \hfill  \addr{hieu@moses-mt.org}\\ 
        \addr{Moses Machine Translation CIC, UK}
\AND
       \name{\bf Nicolay Bogoychev} \hfill \addr{s1031254@sms.ed.ac.uk}\\
       \name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
        \addr{University of Edinburgh, Scotland}
\AND
       \name{\bf Lane Schwartz} \hfill \addr{lanes@illinois.edu}\\
        \addr{University of Illinois, USA}
\AND
       \name{\bf Marcin Junczys-Dowmunt} \hfill \addr{junczys@amu.edu.pl}\\
        \addr{Adam Mickiewicz University}
}
